---
title: "PSY 8712 Week 8 Project"
author: "Sarah Nakamoto"
output: 
  html_document:
    df_print: paged
---

## **Reproducible Image and Online Resources:**

An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](https://mybinder.org/v2/gh/nakam087/psy8712-week8/HEAD?urlpath=rstudio). An interactive web app is available by [clicking this link instead](https://chiems.shinyapps.io/shiny_week8/).

## **Script Settings and Resources**

```{r message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(shiny)
```

## **Data Import and Cleaning**

Here I have cleaned the week3.csv similarly to the previous week relabeled the columns, recoded gender as a factor, and reverse coded q5. Then, I created new variables displaying means of q1:q6 and q8:q10.

```{r}
week8_tbl <- read_csv("../data/week3.csv")%>%
  mutate(timeStart=ymd_hms(timeStart))%>%
  mutate(gender=recode_factor(gender, "M"="Male","F"="Female"))%>% 
  mutate(q5=6-q5)%>%
  rowwise()%>%
  mutate(q1q6_mean=mean(c(q1,q2,q3,q4,q5,q6)))%>%
  mutate(q8q10_mean=mean(c(q8,q9,q10)))
```

## **Visualization**

I selected question 1 through question 6 of week8_tbl, and changed the yaml header to make it so that when displayed, the data was paginated. For the graph, I made a scatterplot and specified the line to be lm method and the color purple, making the standard error band visible.

```{r echo=F}
week8_tbl%>%
  select(q1:q6)
```

```{r echo=F, message=F}
week8_tbl%>%
  ggplot(aes(q1q6_mean,q8q10_mean))+
  geom_point()+
  geom_smooth(method="lm", color="purple")+
  labs(x="Q1 - Q6 means", y="Q8 - Q10 means")

```

## **Analysis**

I had to write the cor.test code without using a pipe because it was not a tidyverse function. I also used a combination of the str_remove and round functions to make sure the decimal did not have a zero in the ones place ("\^0") and was rounded to the hundredths place.

```{r echo=F}
(correlation<-cor.test(x=week8_tbl$q1q6_mean,y=week8_tbl$q8q10_mean))

cor<- correlation$estimate%>%
  round(2)%>%
  str_remove(pattern="^0")
```

I observed a correlation of `r cor`. Because the p value (`r correlation$p.value`) is greater than alpha=0.05, we fail to reject the null hypothesis and thus the true correlation is not significantly different from zero. Thus, answers from q1-q6 are not significantly correlated with answers from q8-q10.

## **Data Export ** 

I used select to choose the important elements from week8_tbl, and then used saveRDS to save the file in the shiny folder.
```{r}
week8_tbl %>%
  select(timeEnd,gender,q1q6_mean,q8q10_mean) %>%
  saveRDS("../shiny_week8/data.rds")
```

